RDF Validation Requirements - Evaluation and Logical Underpinning

### 2014-12-25 paper/RDF validation requirements/RDF validation requirements.tex
mapping tables added

\begin{evaluation}
*Subsumption & \ding{55} & $\checkmark$ & $\checkmark$ & $\sim$ & $\checkmark$ & $\checkmark$ \\
\end{evaluation}

@@

\begin{gcotable}
property & $\exists$ knows . Self & knows & - & Self & $\exists$ \\
class & $\top$ & - & - & $\top$, $\exists$ knows . Self & \sqsubseteq \\
\end{gcotable}

@@

\begin{gcotable}
property & $\exists$ knows . Self & knows & - & Self & $\exists$ \\
class & $\neg$ $\exists$ knows . Self & - & - & $\exists$ knows . Self & $\neg$ \\
class & $\top$ & - & - & $\top$, $\neg$ $\exists$ knows . Self & \sqsubseteq \\
\end{gcotable}

@@

DSCL (ShEx):
\begin{ex}
<Human> { 
    (  
        foaf:name xsd:string ,
        foaf:givenName xsd:string 
    ) ,
    (
        foaf:mbox IRI ,
        foaf:homepage foaf:Document
    ) }
\end{ex}

@@

\begin{DL}
$A \equiv \forall foaf:name . xsd:string$ \\
$B \equiv \forall foaf:givenName . xsd:string$ \\
$C \equiv A XOR B$ \\
$D \equiv \forall foaf:mbox . xsd:string$ \\
$Human \equiv C \sqcap D$ \\
\end{DL}
\er{Where does this using $foaf:$ in DL come from? We need a description.}

\an{I think we should use the existential quantifier instead of the universal quantifier!?}
\begin{DL}
$A \sqsubseteq \exists name.xsd:string$ \\
$B \sqsubseteq \exists givenName.xsd:string$ \\
$D \sqsubseteq \exists mbox.xsd:string$ \\
$Human \sqsubseteq C \sqcap D$ \\
\end{DL}

@@

\begin{DL}
A $\equiv$ $\exists$ foaf:name . xsd:string \\
B $\equiv$ $\exists$ foaf:givenName . xsd:string \\ 
Human $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
\end{DL}

\er{Let us mark that $foaf:$ occurs here.}

\begin{gcotable}
property & A & foaf:name & - & xsd:string & $\forall$ \\
property & B & foaf:givenName & - & xsd:string & $\forall$ \\
class & $\neg$ A & - & - & A & $\neg$ \\
class & $\neg$ B & - & - & B & $\neg$ \\
class & $\neg$ A $\sqcap$ B & - & - & $\neg$ A, B & $\sqcap$ \\
class & A $\sqcap$ $\neg$ B & - & - & A, $\neg$ B & $\sqcap$ \\
class & Human & - & - & $\neg$ A $\sqcap$ B, A $\sqcap$ $\neg$ B & $\sqcup$ \\
\end{gcotable}

\begin{gcotable}
property & A & foaf:name & - & xsd:string & $\forall$ \\
property & B & foaf:givenName & - & xsd:string & $\forall$ \\
class & Human & - & - & A, B & XOR \\
\end{gcotable}

\er{Unsure what is meant in this example.}

@@

%\tb{ToDo: DL}

\er{Unsure what is meant in this example. Could be instead:}

@@

@@

\begin{DL}
Human $\sqsubseteq$ ($\neg$ E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$ F) \\ 
E $\equiv$ A $\sqcap$ B \\
F $\equiv$ C $\sqcap$ D \\
A $\equiv$ $\forall$ foaf:name . xsd:string \\
B $\equiv$ $\forall$ foaf:givenName . xsd:string \\ 
C $\equiv$ $\forall$ foaf:mbox . IRI \\
D $\equiv$ $\forall$ foaf:homepage . foaf:Document \\
\end{DL}

@@

>>>>

@@

\begin{gcotable}
property & $\exists$ knows . Self & knows & - & Self & $\exists$ \\
class & $\top$ & - & - & $\top$, $\exists$ knows . Self & $\sqsubseteq$ \\
\end{gcotable}

@@

\begin{gcotable}
property & $\exists$ knows . Self & knows & - & Self & $\exists$ \\
class & $\neg$ $\exists$ knows . Self & - & - & $\exists$ knows . Self & $\neg$ \\
class & $\top$ & - & - & $\top$, $\neg$ $\exists$ knows . Self & $\sqsubseteq$ \\
\end{gcotable}

@@

\begin{ex}
# ShEx
# ----
<Human> { 
    (  
        foaf:name xsd:string ,
        foaf:givenName xsd:string 
    ) ,
    (
        foaf:mbox IRI ,
        foaf:homepage foaf:Document
    ) }
\end{ex}

@@

%\begin{DL}
%$Human \equiv C \sqcap F$ \\
%$C \equiv A \sqcap B$ \\
%$A \sqsubseteq \exists name.xsd:string$ \\
%$B \sqsubseteq \exists givenName.xsd:string$ \\
%$F \equiv D \sqcap E$ \\
%$D \sqsubseteq \exists mbox.xsd:string$ \\
%$E \sqsubseteq \exists homepage.Document$ \\
%\end{DL}

\begin{DL}
Human $\equiv$ M $\sqcap$ N \\
M $\equiv$ C $\sqcap$ F \\
C $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
F $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
N $\equiv$ I $\sqcap$ L \\
I $\sqsubseteq$ $\geq$ 1 mbox . string $\sqcap$ $\leq$ 1 mbox . string \\
L $\sqsubseteq$ $\geq$ 1 homepage . Document $\sqcap$ $\leq$ 1 homepage . Document \\
\end{DL}

\begin{gcotable}
class & Human & - & - & M, N & $\sqcap$ & - \\
\hline
class & M & - & - & C, F & $\sqcap$ & - \\
class & C & - & - & A, B & $\sqcap$ & - \\
property & A & foaf:name & - & string & $\geq$ & 1 \\
property & B & foaf:name & - & string & $\leq$ & 1 \\
class & F & - & - & D, E & $\sqcap$ & - \\
property & D & foaf:givenName & - & string & $\geq$ & 1 \\
property & E & foaf:givenName & - & string & $\leq$ & 1 \\
\hline
class & N & - & - & I, L & $\sqcap$ & - \\
class & I & - & - & G, H & $\sqcap$ & - \\
property & G & foaf:mbox & - & string & $\geq$ & 1 \\
property & H & foaf:mbox & - & string & $\leq$ & 1 \\
class & L & - & - & J, K & $\sqcap$ & - \\
property & J & foaf:homepage & - & foaf:Document & $\geq$ & 1 \\
property & K & foaf:homepage & - & foaf:Document & $\leq$ & 1 \\
\end{gcotable}

@@

\begin{DL}
Human $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
\end{DL}

\begin{gcotable}
class & Human & - & - & $\neg$ A $\sqcap$ B, A $\sqcap$ $\neg$ B & $\sqcup$ \\
\hline
class & A $\sqcap$ $\neg$ B & - & - & A, $\neg$ B & $\sqcap$ \\
class & $\neg$ A $\sqcap$ B & - & - & $\neg$ A, B & $\sqcap$ \\
\hline
class & $\neg$ A & - & - & A & $\neg$ \\
class & A & - & - & $\geq$ 1 name.string, $\leq$ 1 name.string & $\sqcap$ & - \\
property & $\geq$ 1 name.string & name & - & string & $\geq$ & 1 \\
property & $\leq$ 1 name.string & name & - & string & $\leq$ & 1 \\
\hline
class & $\neg$ B & - & - & B & $\neg$ \\
class & B & - & - & $\geq$ 1 givenName.string, $\leq$ 1 givenName.string & $\sqcap$ & - \\
property & $\geq$ 1 givenName.string & givenName & - & string & $\geq$ & 1 \\
property & $\leq$ 1 givenName.string & givenName & - & string & $\leq$ & 1 \\
\end{gcotable}

syntactic sugar:
\begin{gcotable}
property & = 1 name.string & name & - & string & = & 1 \\
property & = 1 givenName.string & givenName & - & string & = & 1 \\
class & Human & - & - & = 1 name.string, = 1 givenName.string & XOR \\
\end{gcotable}

@@

@@

\begin{DL}
Human $\sqsubseteq$ A $\sqcup$ B \\
A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
\end{DL}

syntactic sugar:
\begin{gcotable}
property & = 1 name.string & name & - & string & = & 1 \\
property & = 1 givenName.string & givenName & - & string & = & 1 \\
class & Human & - & - & = 1 name.string, = 1 givenName.string & $\sqcup$ \\
\end{gcotable}

@@

\begin{DL}
Human $\sqsubseteq$ ($\neg$ E $\sqcap$ F) $\sqcup$ (E $\sqcap$ $\neg$ F) \\ 
E $\equiv$ A $\sqcap$ B \\
F $\equiv$ C $\sqcap$ D \\
A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
C $\sqsubseteq$ $\geq$ 1 mbox . IRI $\sqcap$ $\leq$ 1 mbox . IRI \\
D $\sqsubseteq$ $\geq$ 1 homepage . Document $\sqcap$ $\leq$ 1 homepage . Document \\
\end{DL}

syntactic sugar:
\begin{gcotable}
class & Human & - & - & E, F & XOR \\
class & E & - & - & = 1 name.string, = 1 givenName.string & $\sqcap$ \\
class & F & - & - & = 1 mbox.IRI, = 1 homepage.Document & $\sqcap$ \\
property & = 1 name.string & name & - & string & = & 1 \\
property & = 1 givenName.string & givenName & - & string & = & 1 \\
property & = 1 mbox.IRI & mbox & - & IRI & = & 1 \\
property & = 1 homepage.Document & homepage & - & Document & = & 1 \\
\end{gcotable}

@@

\begin{DL}
Human $\sqsubseteq$ E $\sqcup$ F \\ 
E $\equiv$ A $\sqcap$ B \\
F $\equiv$ C $\sqcap$ D \\
A $\sqsubseteq$ $\geq$ 1 name . string $\sqcap$ $\leq$ 1 name . string \\
B $\sqsubseteq$ $\geq$ 1 givenName . string $\sqcap$ $\leq$ 1 givenName . string \\
C $\sqsubseteq$ $\geq$ 1 mbox . IRI $\sqcap$ $\leq$ 1 mbox . IRI \\
D $\sqsubseteq$ $\geq$ 1 homepage . Document $\sqcap$ $\leq$ 1 homepage . Document \\
\end{DL}

syntactic sugar:
\begin{gcotable}
class & Human & - & - & E, F & $\sqcup$ \\
class & E & - & - & = 1 name.string, = 1 givenName.string & $\sqcap$ \\
class & F & - & - & = 1 mbox.IRI, = 1 homepage.Document & $\sqcap$ \\
property & = 1 name.string & name & - & string & = & 1 \\
property & = 1 givenName.string & givenName & - & string & = & 1 \\
property & = 1 mbox.IRI & mbox & - & IRI & = & 1 \\
property & = 1 homepage.Document & homepage & - & Document & = & 1 \\
\end{gcotable}
